Identifying Equivalent State Bills through Text Reuse. \large Subtitle.

### 2015-10-26 manuscript/text_reuse.tex
added literature on policy diffusion

\subsection{Tasks}
\begin{itemize}
\item Policy diffusion (BD get papers)
\item Text re-use in CBP in bills 
\item Text re-use in general
\begin{itemize}
\item Plaigirism
\item Alignment
\end{itemize} 
\item Discussion of text-based classification
\end{itemize}

In order to detect text reuse between bills we follow \citet{wilderson2015tracing} and use the Smith-Waterman local alignment algorithm \citep{smith1981identification}.

>>>>

Public policy diffusion -- the process by which policymakers emulate the policies implemented outside of their jurisdictions -- is a firmly established area of research in both Comparative \citep{simmons2004,gilardi2009} and American politics \citep{walker1969,berry1990,shipan2006,nicholson-crotty2009}. Until recently, policy diffusion studies have deployed quantitative research designs in which the relational component of policy diffusion (i.e., which jurisdiction is being emulated in a given diffusion instance), has been treated as completely unobservable or assumed to align with the geographic adjacency network (i.e., jurisdictions only emulate their geographic neighbors) \citep{volden2006,boehmke2009}. Recognizing the limitations in this approach, scholars have recently taken on the task of directly measuring the latent networks through which policies diffuse. \cite{desmarais2015} apply network inference algorithms to US state adoption sequences in over 100 policy domains to empirically infer the underlying network through which policies diffuse. \cite{garrett2015} analyze the text of US state legislation to measure the diffusion of policy in one domain -- restrictions on insurance coverage for abortion -- and identify the influence of model legislation, as introduced by interest groups.

In order to detect text reuse between bills we follow \citet{wilkerson2015tracing} and use the Smith-Waterman local alignment algorithm \citep{smith1981identification}.

\subsection{Tasks}
\begin{itemize}
\item Policy diffusion (FL expand paragraph)
\item Text re-use in CBP in bills 
\item Text re-use in general
\begin{itemize}
\item Plaigirism
\item Alignment (FL expand review of Wilkerson et al)
\end{itemize} 
\item Discussion of text-based classification
\end{itemize}
